\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-26 paper.tex
some words

\begin{abstract}
Inter-DataCenter Wide Area Network (Inter-DC WAN) that connects geographically distributed data centers is becoming one of the most critical network infrastructures.
%Network failures are common in WANs, so the provision of high availability has been a major focus of network research.
Due to the limited bandwidth resources and inevitable link failures, it is highly challenging to guarantee network availability for services, especially those with stringent bandwidth demands, over inter-DC WAN.
%While modern datacenter services increasingly call for high availability, network failures in WANs remain a fairly common phenomenon.
%Most traffic engineering schemes only consider connectivity-based availability and this severely degrades quality of service, thus revenue.
We present $\mathsf{BATE}$,
a novel Traffic Engineering (TE)  framework that 
%contains admission control, online scheduling and failure recovery.
aims for \textit{bandwidth availability} (BA) provision, where a service level agreement (SLA) defines that a demand on certain bandwidth should be satisfied with a stipulated probability,  when subjected to the network capacity and possible failures of the inter-DC WAN.
%Also, $\mathsf{BATE}$ is able to maximize revenue when network fails.
%$\mathsf{BATE}$ tries to guarantee the bandwidth-based availability of demands . 
%$\mathsf{BATE}$ generates a probabilistic failure model from empirical data and maximizes the profit that can be achieved under certain constrains on  bandwidth-based availability. 
%For the failure model, we propose a pruning algorithm to reduce the problem size.
%For the optimization problem, we prove it is NP-hard and  propose a greedy algorithm to efficiently solve it with only minor profit loss. 
%We design and implement an SDN-based system named $\mathsf{Dionysus}$ to deploy $\mathsf{BATE}$ over inter-DC WAN.
The three core components of  $\mathsf{BATE}$, i.e., admission control, traffic scheduling and failure recovery, are built on different mathematical models and theoretically analyzed. 
They are also extensively compared against state-of-the-art TE schemes, using testbed as well as trace driven simulations across different topologies, traffic matrices and failure scenarios. 
Our evaluation demonstrates that, compared with the optimal admission strategy, $\mathsf{BATE}$ can speed up the online admission control by 30$\times$ at the expense of only a xx\% false rejections. 
On the other hand, compared with the latest TE schemes like FFC and TEAVAR,   $\mathsf{BATE}$ can meet the bandwidth availability SLAs for 40\% more demands, and when network failure causes SLA violations, it can retain 25\% more profit  under a simple pricing and refunding model.
%.
% $\mathsf{BATE}$ can 
%(1) achieve 30 $\times$ speedup in admission control time at the expense of sacrificing 8\% in performance compared to the optimal stragety;
%(2) increase the percentage of demands that satisfy their availability SLAs by up to 40\%;
%(3) hold 30\% more profit for the provider when network fails. 
%The evaluation results demonstrate that $\mathsf{BATE}$ can make 20\%, 25\%, 30\%, 40\% more flows satisfy their bandwidth-based availability demands  than TEAVAR, SMORE, SWAN and FFC, respectively.
\end{abstract}

@@

Thirdly, 
we implement $\mathsf{BATE}$ as a real system, including a centralized controller and multiple brokers (one for each DC),  together with end-host clients (see $\S$\ref{system}).
 We conduct extensive experiments using a small testbed as well as trace driven large scale simulations (see $\S$\ref{evaluation}).
We compare  $\mathsf{BATE}$ with state-of-the-art WAN TE schemes such as TEAVAR \cite{Teavar}, SMORE \cite{SMORE}, SWAN \cite{swan}, B4 \cite{B4} and FFC \cite{FFC}, across different topologies, traffic matrices and failure scenarios.
Our evaluation demonstrates that $\mathsf{BATE}$ can 
(1) speed up the online admission control by 30$\times $ at the expense of a false rejection ratio that is only around xx\%;
(2) meet the bandwidth availability SLAs for 40\% more demands;
(3) retain 25\% more profit when network failure causes SLA violations, under a simple pricing and refunding model. 
To our knowledge, $\mathsf{BATE}$ is the first to tackle bandwidth availability provision over inter-DC WAN, where heterogeneities of demands and link failures are systematically taken into account for profit maximization.  
 %At last, we show the related works (see $\S$\ref{relate}).
%Traditionally, links are heavily underutilized to achieve a more rigorous availability target. 
%However, in reality, the failure probability of a single link can even differ by three orders of magnitude.
%Therefore, some link failure can be negligible and it makes no sense to reduce the utilization of these links.
%With the link Under BATE, links can maintain high utilization.

@@

\section{Evaluation} \label{evaluation}
In this section, we use a small testbed and larger scale trace driven simulations  to evaluate the performance of $\mathsf{BATE}$. 
On the testbed, we also implement another two state-of-the-art TE algorithms considering network availability, i.e., FFC \cite{FFC} and TEAVAR \cite{Teavar}. 
For simulation, we implement more TE algorithms, including xxx. 
All codes for our implementation and evaluation will be published, 
so that interested readers can use them in their own environments or make further improvements.

@@

(2) $\mathsf{BATE}$ achieves a good tradeoff between efficiency and optimality. 
Compared with the optimal solutions, (i) our admission control algorithm can speed up the admission procedure by 30$\times$ at the expense of only xx\% false rejections, 
(ii) our pruning-augmented scheduling algorithm runs xx$\times$ faster while wasting only 6\% total bandwidth and losing only 8\% overall availability, 
and (iii) our greedy failure recovery algorithm can reduce the reaction time by xx$\times$, 
where the profit loss is below 10\%.

@@

\textit{Traffic scheduling.} We evaluate, once a user demand is admitted, 
how often its bandwidth availability requirement can be guaranteed. 
Since we emulate different link failures according to their probabilities in each second, 
we can measure how the bandwidth a user actually uses deviates from its requirement. 
If such a deviation is less than 1\%, we regard the bandwidth availability as \textit{satisfied in that second}. Figure \ref{e2}(b) shows the overall fraction of satisfaction, under  different levels of availability requirements (i.e., 95\%, 99\% and 99.99\%). 
We note that, FFC-fixed (or TEAVAR-fixed) in the figure represents applying FFC (or TEAVAR) 
only to demands admitted by the fixed admission control strategy, 
where the total bandwidth required for the admitted demands will be much lower. 
$\mathsf{BATE}$ always achieves the highest availability, even compared with FFC-fixed and TEAVAR-fixed. 
In particular, it has a clear advantage for high availability requirements (e.g., >99.99\%). 
%To further illustrate the difference in their mechanisms,

\textit{Failure Recovery.} We evaluate when failures do occur and cause SLA violations, 
how profit loss can be mitigated by our failure recovery scheme.
Figure \ref{e2}(c) depicts the fraction of profit loss caused by SLA violations under three different admission control strategies, i.e., fixed, BATE-AD (which is the strategy $\mathsf{BATE}$ uses) and optimal, where baseline for each algorithm is the profit it can achieve when no failures occur. 
%\textbf{TBD: $\mathsf{BATE}$ can retain about 15\% more money ratio than FFC and TEAVAR when network fails.}
Compared with TEAVAR, FFC has a lower profit loss ratio due to its conservative bandwidth allocation.

\textit{Overall Profit.}
Figure \ref{e2}(d) plots the overall profit gain comparison among $\mathsf{BATE}$, FFC and TEAVAR  for all arrived demands.
Thanks to the hard guarantee of bandwidth availability and optimization of profit gain after failures, $\mathsf{BATE}$ can maintain at least 15\% more profit than  FFC and TEAVAR.

Due to space limitations, more details of the evaluations are shown in  Appendix \ref{testbed-appendix}.

@@

\textbf{Evaluations on parallel demands.}
Now we use another example with three user demands to illustrate more details of $\mathsf{BATE}$. 
In our evaluation, we also compare with another scheme named BATE-TE, i.e, the traffic scheduling part of $\mathsf{BATE}$, with its fast failure recovery scheme abandoned. 
Demand-1 requires 1000Mbps from DC1 to DC3, demand-2 requires  500Mbps from DC1 to DC4, 
and demand-3 requires 1500Mbps from DC1 to DC5, 
with their availability target set as 99.5\%, 99.9\% and 95\%, respectively. 
We start their traffic simultaneously, assuming all of them have been admitted, 
and their bandwidth on each path, as shown in Table \ref{testbed-1}, 
is determined by different TE algorithms. 
The experiment lasts 100s and is repeated by 100 times.
Figure \ref{e1}(a) shows the fraction of time each bandwidth availability demand is satisfied, 
using the same method as in Figure \ref{e2}(a), i.e, for each second, 
a gap of more than 1\% bandwidth means the demand is not satisfied in that slot. 
It shows that all the three demands can reach their availability targets under $\mathsf{BATE}$,
while TEAVAR and FFC may fail for some users. 
With an investigation on the bandwidth allocation result in Table \ref{testbed-1}, 
we can see that, FFC reserves too much bandwidth for failure recovery, 
so that demand-1 never gets enough bandwidth (250 Mbps allocated v.s. 1500 Mbps demanded), 
and its achieved bandwidth availability is always 0. 
Even it allocates enough bandwidth for demand-2, the achieved bandwidth availability (98.2\%)  
is still lower than required (99.9\%). 
On the other hand, TEAVAR does not make a good match between the link failure probability and the availability users ask for. 
For example, for demand-2, which needs the highest level of availability (99.9\%), 
TEAVAR still allocates 250 Mbps on link L4, which has the highest failure probability (1\%) 
\footnote{In Figure \ref{e1}(b), we plot the actual number of failures that occur in the 100 experiments, 
where L4 fails most frequently.}. 
On the contrary, $\mathsf{BATE}$ matches demands and links well, and does not use L4 for user-2.
%Another factor we must pay attention into is the

@@

\subsection{Simulations}
\textbf{Simulation setup.} 
We also conduct simulations on four real network topologies, including B4 \cite{B4}, ATT \cite{Teavar}, IBM\cite{SMORE} and a national-level backbone. 
Table \ref{evaluation-topologies} shows the topology details
\footnote{For B4, ATT and IBM, we get their topologies, link capacities and traffic matrices from the authors of TEAVAR\cite{Teavar}, and for the national backbone, we conduct a direct measurement on it but hide its name due to anonymity requirement.}. 
Following the conclusion on WAN failures in literature studies\cite{Characterization, Teavar}, 
we simulate link failures according to a Weibull distribution with its shape $\lambda=0.8$ and scale $k=0.00001$. 
We generate the demand workload in a similar way to that in the testbed. 
The arrivals of BA demands follow a Poisson process, with a mean inter-arrival time of 2 minutes. 
The duration of each demand follows an exponential distribution, and the mean duration corresponds to 1000 time slots.
The required bandwidth in each user demand is randomly drawn from the traffic metrices (we have collected 200 matrices for each topology) with a proper scale down factor (we use 5), so that between each source-destination pair, multiple users can be served simultaneously. 
The required availability in each user demand is drawn from 10 different SLAs of Azure\cite{azure}.
In our simulations, besides FFC and TEAVAR, we also compare against several other TE algorithms,  
including SWAN \cite{swan}, SMORE \cite{SMORE} and B4 \cite{B4}. 
They have not explicitly considered availability, but pay attention to 
total throughput, link utilization or user fairness. 
These TE algorithms will be activated every 10 time slots.
We assume at most one link failure (i.e., no concurrent failures) in FFC,  
use 99.9\% (the maximum value in the user demands) as the default availability target in TEAVAR,
and let SWAN maximize the total throughput of all users. 
With the above settings, each simulation lasts 150,000 slots (corresponding to 100 days if each slot represents 1 minute), and the results that achieved by each algorithm on each topology are calculated on 5 independent simulations with different workload traces.

@@

\textbf{Evaluation results.}
%From the comparison between the scheduled and testbed results, we can see that the scheduled results match the real testbed quite well,
%so in the following part, we will use trace-driven simulation to evaluate the performance of $\mathsf{BATE}$.

%
%
%
%
%
%
%
 \begin{figure}[h]
\begin{center}
\includegraphics [width=0.7\columnwidth] {fig/evaluation/sim-monney.pdf}
\caption{Profit gain after failures}
\label{sim-profit}
\end{center}
\end{figure}

@@

Figure \ref{availability_fig1}(a)  shows $\mathsf{BATE}$  rejects only about 3\% more demands than the optimal solution and can accept up to 50\% more demands than the \textit{Fixed} consistently.
Figure \ref{availability_fig1}(b) demonstrates  $\mathsf{BATE}$ is able to maintain at least 10\% higher link utilization than \textit{Fixed} algorithm.
We qualify the scalability by measuring the admission control time for each demand.
The simulation is performed on a Linux server (4-core, 2.60GHz processor with 32GB).
As shown in Figure \ref{availability_fig1}(c), the admission control time of $\mathsf{BATE}$ is less than 1s with about less than 5\% error, which is at least 30$\times$ faster the global optimal solution.

@@

As more applications are depolyed in cloud or datacenters, 
many work study how to provide performance guarantee for intra-DC or inter-DC user traffic, 
including flow deadline \cite{D2TCP, LPD, Guaranteeings} and flow rate \cite{appdriven, EyeQ}.
However, they do not provide adquate mechanisms to deal with potential or actual failures.

@@

We measure total bytes loss according to \textit{iperf} server side reports and packet counters in the switches, then finally derive the data loss ratio.
Figure \ref{e2}(d) demonstrates data loss ratio after network fails, where $\mathsf{BATE}$ performs about 8\% worse than FFC.
FFC performs best since it keeps network utilization low and almost no congestion occurs when network fails, 
while $\mathsf{BATE}$ focuses on Monetary gain rather than data loss.

>>>>

\begin{abstract}
Inter-DataCenter Wide Area Network (Inter-DC WAN) that connects geographically distributed data centers is becoming one of the most critical network infrastructures.
%Network failures are common in WANs, so the provision of high availability has been a major focus of network research.
Due to the limited bandwidth resources and inevitable link failures, it is highly challenging to guarantee network availability for services, especially those with stringent bandwidth demands, over inter-DC WAN.
%While modern datacenter services increasingly call for high availability, network failures in WANs remain a fairly common phenomenon.
%Most traffic engineering schemes only consider connectivity-based availability and this severely degrades quality of service, thus revenue.
We present $\mathsf{BATE}$,
a novel Traffic Engineering (TE)  framework that 
%contains admission control, online scheduling and failure recovery.
aims for \textit{bandwidth availability} (BA) provision, where a service level agreement (SLA) defines that a demand on certain bandwidth should be satisfied with a stipulated probability,  when subjected to the network capacity and possible failures of the inter-DC WAN.
%Also, $\mathsf{BATE}$ is able to maximize revenue when network fails.
%$\mathsf{BATE}$ tries to guarantee the bandwidth-based availability of demands . 
%$\mathsf{BATE}$ generates a probabilistic failure model from empirical data and maximizes the profit that can be achieved under certain constrains on  bandwidth-based availability. 
%For the failure model, we propose a pruning algorithm to reduce the problem size.
%For the optimization problem, we prove it is NP-hard and  propose a greedy algorithm to efficiently solve it with only minor profit loss. 
%We design and implement an SDN-based system named $\mathsf{Dionysus}$ to deploy $\mathsf{BATE}$ over inter-DC WAN.
The three core components of  $\mathsf{BATE}$, i.e., admission control, traffic scheduling and failure recovery, are built on different mathematical models and theoretically analyzed. 
They are also extensively compared against state-of-the-art TE schemes, using testbed as well as trace driven simulations across different topologies, traffic matrices and failure scenarios. 
Our evaluation demonstrates that, compared with the optimal admission strategy, $\mathsf{BATE}$ can speed up the online admission control by 30$\times$ at the expense of less than 4\% false rejections. 
On the other hand, compared with the latest TE schemes like FFC and TEAVAR,   $\mathsf{BATE}$ can meet the bandwidth availability SLAs for 40\% more demands, and when network failure causes SLA violations, it can retain 25\% more profit  under a simple pricing and refunding model.
%.
% $\mathsf{BATE}$ can 
%(1) achieve 30 $\times$ speedup in admission control time at the expense of sacrificing 8\% in performance compared to the optimal stragety;
%(2) increase the percentage of demands that satisfy their availability SLAs by up to 40\%;
%(3) hold 30\% more profit for the provider when network fails. 
%The evaluation results demonstrate that $\mathsf{BATE}$ can make 20\%, 25\%, 30\%, 40\% more flows satisfy their bandwidth-based availability demands  than TEAVAR, SMORE, SWAN and FFC, respectively.
\end{abstract}

@@

Thirdly, 
we implement $\mathsf{BATE}$ as a real system, including a centralized controller and multiple brokers (one for each DC),  together with end-host clients (see $\S$\ref{system}).
 We conduct extensive experiments using a small testbed as well as trace driven large scale simulations (see $\S$\ref{evaluation}).
We compare  $\mathsf{BATE}$ with state-of-the-art WAN TE schemes such as TEAVAR \cite{Teavar}, SMORE \cite{SMORE}, SWAN \cite{swan}, B4 \cite{B4} and FFC \cite{FFC}, across different topologies, traffic matrices and failure scenarios.
Our evaluation demonstrates that $\mathsf{BATE}$ can 
(1) speed up the online admission control by 30$\times $ at the expense of a false rejection ratio that is less than 4\%;
(2) meet the bandwidth availability SLAs for 40\% more demands;
(3) retain 25\% more profit when network failure causes SLA violations, under a simple pricing and refunding model. 
To our knowledge, $\mathsf{BATE}$ is the first to tackle bandwidth availability provision over inter-DC WAN, where heterogeneities of demands and link failures are systematically taken into account for profit maximization.  
 %At last, we show the related works (see $\S$\ref{relate}).
%Traditionally, links are heavily underutilized to achieve a more rigorous availability target. 
%However, in reality, the failure probability of a single link can even differ by three orders of magnitude.
%Therefore, some link failure can be negligible and it makes no sense to reduce the utilization of these links.
%With the link Under BATE, links can maintain high utilization.

@@

\section{Evaluation} \label{evaluation}
In this section, we use a small testbed and larger scale trace driven simulations  to evaluate the performance of $\mathsf{BATE}$. 
On the testbed, we also implement another two state-of-the-art TE algorithms considering network availability, i.e., FFC \cite{FFC} and TEAVAR \cite{Teavar}. 
For simulation, we implement more TE algorithms, including SWAN \cite{swan}, SMORE \cite{SMORE} and B4 \cite{B4}. 
All codes for our implementation and evaluation will be published, 
so that interested readers can use them in their own environments or make further improvements.

@@

(2) $\mathsf{BATE}$ achieves a good tradeoff between efficiency and optimality. 
Compared with the optimal solutions, (i) our admission control algorithm can speed up the admission procedure by 30$\times$ at the expense of less than 4\% false rejections, 
(ii) our pruning-augmented scheduling algorithm runs xx$\times$ faster while wasting only 6\% total bandwidth and losing only 8\% overall availability, 
and (iii) our greedy failure recovery algorithm can reduce the reaction time by xx$\times$, 
where the profit loss is below 10\%.

@@

\textit{Traffic scheduling.} We evaluate, once a user demand is admitted, 
how often its bandwidth availability target can be met. 
Since we emulate different link failures according to their probabilities in each second, 
we can measure how the bandwidth a user actually uses deviates from its requirement. 
If such a downward deviation is less than 1\%, we regard the bandwidth availability as \textit{satisfied in that second}. Figure \ref{e2}(b) shows the overall fraction of satisfaction, under  different levels of availability requirements (i.e., 95\%, 99\% and 99.99\%). 
We note that, FFC-fixed (or TEAVAR-fixed) in the figure represents applying FFC (or TEAVAR) 
only to demands admitted by the fixed admission control strategy, 
where the total bandwidth required for the admitted demands is much lower. 
$\mathsf{BATE}$ always achieves the highest availability, even compared with FFC-fixed and TEAVAR-fixed. 
In particular, it has a clear advantage for high availability requirements (e.g., >99.99\%). 
%To further illustrate the difference in their mechanisms,

\textit{Failure Recovery.} We evaluate when failures do occur and cause SLA violations, 
how profit loss can be mitigated by our failure recovery scheme.
Figure \ref{e2}(c) depicts the fraction of profit loss caused by SLA violations under three different admission control strategies, i.e., fixed, BATE-AD (which is the strategy $\mathsf{BATE}$ uses) and optimal, where baseline for each algorithm is the profit it can achieve when no failures occur. 
%\textbf{TBD: $\mathsf{BATE}$ can retain about 15\% more money ratio than FFC and TEAVAR when network fails.}
$\mathsf{BATE}$ always achieves the lowest loss ratio, while 
FFC also has a lower profit loss ratio due to its conservative bandwidth allocation,
and TEAVAR may cause around 5$\times$ higher profit loss.

\textit{Overall Profit.}
Figure \ref{e2}(d) plots the overall profit of $\mathsf{BATE}$, FFC and TEAVAR.
Due to its hard guarantee on bandwidth availability and its  profit maximization, 
$\mathsf{BATE}$ can achieve at least 15\% more profit than the other two.

Due to space limitations, more details of the evaluations, including the the ratio of the
allocated bandwidth to the demanded bandwidth, and the actual data loss ratio, 
are put into  Appendix \ref{testbed-appendix}.

@@

\textbf{Evaluations on parallel demands.}
Now we use another example with three parallel user demands to illustrate more details of $\mathsf{BATE}$. 
In this evaluation, we also compare with another scheme named BATE-TE, i.e, the traffic scheduling part of $\mathsf{BATE}$, with its fast failure recovery scheme abandoned. 
Demand-1 requires 1000Mbps from DC1 to DC3, demand-2 requires  500Mbps from DC1 to DC4, 
and demand-3 requires 1500Mbps from DC1 to DC5, 
with their availability target set as 99.5\%, 99.9\% and 95\%, respectively. 
We start their traffic simultaneously, assuming all of them have been admitted, 
and their bandwidth on each path, as shown in Table \ref{testbed-1}, 
is determined by different TE algorithms. 
The experiment lasts 100s and is repeated by 100 times.
Figure \ref{e1}(a) shows the fraction of time each bandwidth availability demand is satisfied, 
using the same method as in Figure \ref{e2}(a), i.e, for each second, 
a gap of more than 1\% bandwidth means the demand is not satisfied in that slot. 
It shows that all the three demands can reach their availability targets under $\mathsf{BATE}$,
while TEAVAR and FFC may fail for some users. 
With an investigation on the bandwidth allocation result in Table \ref{testbed-1}, 
we can see that, FFC reserves too much bandwidth for failure recovery, 
so that demand-1 never gets enough bandwidth (250 Mbps allocated v.s. 1500 Mbps demanded), 
and its achieved bandwidth availability is always 0. 
Even it allocates enough bandwidth for demand-2, the achieved bandwidth availability (98.2\%)  
is still lower than required (99.9\%). 
On the other hand, TEAVAR does not make a good match between the link failure probability and the availability users ask for. 
For example, for demand-2, which needs the highest level of availability (99.9\%), 
TEAVAR still allocates 250 Mbps on link L4, which has the highest failure probability (1\%) 
\footnote{In Figure \ref{e1}(b), we plot the actual number of failures that occur in the 100 experiments, 
where L4 fails most frequently.}. 
On the contrary, $\mathsf{BATE}$ matches demands and links well, and does not use L4 for user-2.
%Another factor we must pay attention into is the

@@

\subsection{Simulations}
\textbf{Simulation setup.} 
We also conduct simulations on four real network topologies, including B4 \cite{B4}, ATT \cite{Teavar}, IBM\cite{SMORE} and a national-level backbone. 
Table \ref{evaluation-topologies} shows the topology details
\footnote{For B4, ATT and IBM, we get their topologies, link capacities and traffic matrices from the authors of TEAVAR\cite{Teavar}, and for the national backbone, we conduct a direct measurement on it but hide its name due to anonymity requirement.}. 
Following the conclusion on WAN failures in literature studies\cite{Characterization, Teavar}, 
we simulate link failures according to a Weibull distribution with its shape $\lambda=0.8$ and scale $k=0.00001$. 
We generate the demand workload in a similar way to that in the testbed. 
The arrivals of BA demands follow a Poisson process, with a mean inter-arrival time of 2 minutes. 
The duration of each demand follows an exponential distribution, and the mean duration corresponds to 1000 time slots.
The required bandwidth in each user demand is randomly drawn from the traffic metrices (we have collected 200 matrices for each topology) with a proper scale down factor (we use 5), so that between each source-destination pair, multiple users can be served simultaneously. 
The required availability in each user demand is drawn from 10 different SLAs of Azure\cite{azure}.
In our simulations, besides FFC and TEAVAR, we also compare against several other TE algorithms,  
including SWAN \cite{swan}, SMORE \cite{SMORE} and B4 \cite{B4}. 
They have not explicitly considered availability, but pay attention to 
total throughput, link utilization or user fairness. 
These TE algorithms will be activated every 10 time slots.
We assume at most one link failure (i.e., no concurrent failures) in FFC,  
use 99.9\% (which is the maximum value in the user demands) as the default availability target in TEAVAR,
and let SWAN maximize the total throughput of all users. 
With the above settings, each simulation lasts 150,000 slots (corresponding to 100 days if each slot represents 1 minute), and the results achieved by each algorithm on each topology are calculated on 5 independent simulations with different workload traces.

@@

%From the comparison between the scheduled and testbed results, we can see that the scheduled results match the real testbed quite well,
%so in the following part, we will use trace-driven simulation to evaluate the performance of $\mathsf{BATE}$.

%
%
%
%
%
%
%

@@

\textbf{Evaluation results.}
\begin{figure}[h]
\begin{center}
\includegraphics [width=0.7\columnwidth] {fig/evaluation/sim-monney.pdf}
\caption{Profit gain after failures}
\label{sim-profit}
\end{center}
\end{figure}
Figure \ref{availability_fig1}(a)  shows $\mathsf{BATE}$  rejects only about 3\% more demands than the optimal solution and can accept up to 50\% more demands than the \textit{Fixed} consistently.
Figure \ref{availability_fig1}(b) demonstrates  $\mathsf{BATE}$ is able to maintain at least 10\% higher link utilization than \textit{Fixed} algorithm.
We qualify the scalability by measuring the admission control time for each demand.
The simulation is performed on a Linux server (4-core, 2.60GHz processor with 32GB).
As shown in Figure \ref{availability_fig1}(c), the admission control time of $\mathsf{BATE}$ is less than 1s with about less than 5\% error, which is at least 30$\times$ faster the global optimal solution.

@@

As more applications are depolyed in cloud or datacenters, 
many work study how to provide performance guarantee for intra-DC or inter-DC user traffic, 
including flow deadline \cite{D2TCP, LPD, Guaranteeings},  flow rate \cite{appdriven, EyeQ}, etc.
However, they do not provide adquate mechanisms to deal with potential or actual failures.

@@

Data loss due to failures is measured according to statistics reported by \textit{iperf} and switches.
As shown in Figure \ref{e2}(d), there is almost no loss in FFC, since it keeps a low network utilization. 
$\mathsf{BATE}$ has a slight loss caused by , while TEAVAR has the highest loss. 
\end{appendices}
